### 2021-09-09 article/article.tex
update

\subsection{NSI phenomenology at probability level}\label{sec:nsiProbEffects}
Since neutrinos and antineutrinos have different cross sections, they are treated separately in the detector simulations. 
However, for the purpose of qualitatively elucidating the NSI effect in this subsection, we take the effective area of $\nm$ and $\anm$ to be equal. 
Thus, we simply add the neutrino to the antineutrino contributions in both Fig.~\ref{fig:nsi_probs} and Fig.~\ref{fig:flux_ratio}.

In the $\mu\tau$ sector, we have a resonance in the \SI{20}{\GeV} region. Any NSI parameter involving the $\mu$ or $\tau$ channel will dampen this resonance,
with some also shifting the probability in the stationary region above \SI{100}{\GeV}.
This `double effect' of both resonance dampening and shifting happens in two cases: either when the NSI parameter shares one channel with a survival probability
(e.g. $\eem$ and $P_{\mu\mu}$), or when the sectors align (e.g. $\emt$ and $P_{\mu\tau}$). The only exception to this is for $P_{\tau\tau}$, 
which due to the near-maximal mixing in the $\mu\tau$ sector displays dampening for $\eem$ even though they share no channel directly. We illustrate
the three different effects in Fig.~\ref{fig:nsi_probs}.

Due to the lightness of $\Delta m^2_{21}$, the $e$ channel has no resonance in the \si{\GeV} range. Thus, the only impact that 
the NSI parameters considered here can have on any $\nu_e$ probability is shifting, and this only occurs when the requirements for the `double effect'
are met. So except for the survival probability $P_{ee}$, any NSI parameter whose sector does not match the probability sector will not drastically affect it. 
Thus, the only off-diagonal NSI parameters that strongly affect the transition probabilities $P_{\alpha\beta}$ are $\epsilon_{\gamma\beta}$,
while the survival probabilities $P_{\alpha\alpha}$ are only strongly affected by $\epsilon_{\alpha\beta}$.
%TODO: make this clearer and give conclusion. Maybe also test for lower E around dm21 resonance. Add about realness and CP-invariance
\begin{figure}
   \includegraphics[width=0.95\textwidth]{figures/nsi_probs.pdf}
   \caption{The three different effects that the off-diagonal NSI parameters have in 
   the \si{\GeV} range. To schematically elucidate the NSI effect, we plot the summed probabilities for both neutrinos and 
   antineutrinos.}\label{fig:nsi_probs}
\end{figure}%TODO: change plot ylabels

>>>>

\subsection{NSI phenomenology at probability level}\label{sec:nsiProbEffects}
% Since neutrinos and antineutrinos have different cross sections, they are treated separately in the detector simulations. 
% However, for the purpose of qualitatively elucidating the NSI effect in this subsection, we take the effective area of $\nm$ and $\anm$ to be equal. 
% Thus, we simply add the neutrino to the antineutrino contributions in both Fig.~\ref{fig:nsi_probs} and Fig.~\ref{fig:flux_ratio}.

% In the $\mu\tau$ sector, we have a resonance in the \SI{20}{\GeV} region. Any NSI parameter involving the $\mu$ or $\tau$ channel will dampen this resonance,
% with some also shifting the probability in the stationary region above \SI{100}{\GeV}.
% This `double effect' of both resonance dampening and shifting happens in two cases: either when the NSI parameter shares one channel with a survival probability
% (e.g. $\eem$ and $P_{\mu\mu}$), or when the sectors align (e.g. $\emt$ and $P_{\mu\tau}$). The only exception to this is for $P_{\tau\tau}$, 
% which due to the near-maximal mixing in the $\mu\tau$ sector displays dampening for $\eem$ even though they share no channel directly. We illustrate
% the three different effects in Fig.~\ref{fig:nsi_probs}.

% Due to the lightness of $\Delta m^2_{21}$, the $e$ channel has no resonance in the \si{\GeV} range. Thus, the only impact that 
% the NSI parameters considered here can have on any $\nu_e$ probability is shifting, and this only occurs when the requirements for the `double effect'
% are met. So except for the survival probability $P_{ee}$, any NSI parameter whose sector does not match the probability sector will not drastically affect it. 
% Thus, the only off-diagonal NSI parameters that strongly affect the transition probabilities $P_{\alpha\beta}$ are $\epsilon_{\gamma\beta}$,
% while the survival probabilities $P_{\alpha\alpha}$ are only strongly affected by $\epsilon_{\alpha\beta}$.
%TODO: make this clearer and give conclusion. Maybe also test for lower E around dm21 resonance. Add about realness and CP-invariance
\begin{figure}
   \includegraphics[width=0.85\textwidth]{figures/probabilities.pdf}
   \caption{}\label{fig:nsi_probs}
\end{figure}
